Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-29 paper/ms.tex
udpated discussion

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field size by
constructing mock fields from a large cosmological N-body
simulation matching the observational geometries. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
one LAE with a probability $f_{\rm occ}$.  We find that the observational information on the number density restricts the minimum mass to a
range $10^{10}\hMsun < M_{\rm min}< 10^{11.5}\hMsun$ leaving all the
other parameters unrestricted, while the clustering information puts a
tight constraint of $M_{\rm   max}<10^{12}\hMsun$. This gives support
to the idea that the most massive dark matter halos at that epoch do
not host the brightest LAEs.  However, none of these observations is
able to constrain the occupation fraction. It is always possible to
find a model that is consistent with observations and has any desired
occupation fraction in the range $0.1\leq f_{\rm occ}\leq
1.0$. Furthermore, all models have a mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than 1.0 dex. 
We divide the best models into families of low and high occupation
fraction with a transition around $f_{\rm occ}\leq 0.3$. These two
families are almost disjoint in their values of $M_{\rm min}$. Low
occupation fraction occurs below a threshold of $M_{\rm th}=
10^{10.8}\Msun$, while high occupation fractions are present in
$M_{\rm min}>M_{\rm the}$. These two families of models are
similar in size, giving an unconclusive response as to which is the
occupation fraction of LAEs at $z=3.1$. A conclusive answer requires
a detailed physical model for the  connection between dark matter,
star formation and the escape of \ly radiation. That kind of modelling
should also provide a plausible explanation for the narrow range in
mass $\Delta M<1.0$ dex derived here for the halos hosting LAEs at
$z=3.1$.

@@

We note that we use $15\times 12=144$ mock fields out of the total of $210$
available sub-volumes. The reason is that the {\texttt match}
method imposes constraints on the way the $7$ fields mimicking the
SSA22 can be distributed, making unusuable some of the
sub-volumes in the box. We decide to keep the number of mock surveys
fixed to $15$ also for the {\texttt random} method in order to allow a
fair comparison between the two methods.

@@

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
both for the comparisong against \cite{Hayashino2004} and
\cite{Ouchi2010}. To make this selection we consider that
a model is consistent with observations if there is a $1-\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. We clearly see from this Figure that the conditions imposed
by \cite{Hayashino2004} are the tightest. Comparing this Figure with
the results shown in Figure \ref{fig:restriction_mock} we see that
practically all models with $M_{\rm max}>10^{12}$ are removed. On the
other hand the comparison against \cite{Ouchi2010} does not succeed in
greatly reducing the number of models.

At this point we keep the models that are consistent with both
observational constraints. This basically reduces the selection to the
models already restricted by the data in \cite{Hayashino2004} as
presented in the lower panels of Figure
\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
this comparison is that clustering information is able to put
meaningful constraints on the values of $M_{\rm max}$. However, the
possible values for the occupation fraction are still in the initial
range $0.1\leq f_{\rm occ}\leq 1$.

%In order to better illustrate the results from this test we
%show in the right panel of Figure \ref{figure:correlation_parameters} 
%the plane $\theta_{0}$-$M_{\rm min}$ for all models divided in two
%disjoint sets. The first are the models $\log_{10} M_{\rm
%    max}<12$ (blue dots), the second corresponds to $\log_{10} M_{\rm
%    max}>12$ (green dots). The colored rectangle includes
%the parameter region which is consistent with the observational
%constraint in $\theta_{0}$.  With this restriction we find that most

%models with $\log_{10} M_{\rm max}>12$ and  $\log_{10} M_{\rm min}>11.s$ 
%can be safely ruled out.

@@

In the Results Section we start by matching the rough numbers for the
galaxy surface number density. This sets the median mass of all
successful models to the broad range $(10^{10}-10^{12})$ \hMsun for
$M_{\rm min}$ and $M_{\rm max}$. We include additional criteria on the
number of mock surveys that must be consistent observations
and the information from the angular correlation function, reducing
the number of feasible models. We end up with $\sim 50$ models out of
the initial $9000$ possible combination of parameters.

In order to make a physical interpretation of these models we use 
the halo mass range, defined as $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm  min}$, together with the occupation fraction $f_{\rm
  occ}$ to classify all the successful models into three families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$ and low $\Delta M\leq 1.0$
  dex: 24 models.
\item[(2)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
  models
\item[(3)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
\end{itemize}

There is a clear majority of models with a narrow $\Delta M\leq
1$, compared to the $2.5$dex of halo mass available for occupation at
that redshift. Such models imply that there is a cut at lower and higher halo
masses that render inefficient the presence and/or detection of LAEs.

At the low mass end, such cut can be readily interpreted in terms of the
minimal halo star formation rate needed to produce the minimal \ly 
luminosity to be above a given detection threshold.  However, under
the reasonable assumption of star formation rate increasing with halo
mass, the cut at higher halo masses requires a different
justification. There are two complementary physical scenarios that can
provide an explanation.

@@

A second scenario is that larger systems have more extended gaseous
envelopes which. Again, due to resonance effects of the \ly line,
these systems can present a low surface brightness and a broader line,
making these systems less observable in narrow band filter surveys
\citep{Laursen2009,Zheng2010}.

The preference for narrow $\Delta M$ ranges to host LAEs 
and the small presence of reasonable models with $M_{\rm max}>
10^{12}$\hMsun follows theoretical and observational
insights where the most massive systems are not bright \ly sources
\citep{ForeroRomero2012,Shapley2003}.

@@

We also find that $70\%$ of the best models are found in families (1)
and (2), with a low occupation fraction $f_{\rm occ}\leq 0.3$. This
preference goes in the same direction as the observational constraint
on the escape fraction $f_{\rm esc}\sim 0.1-0.2$ derived at $z=2.2$ by
\cite{Hayes2010} and recent theoretical study of observational data in
a wide redshift range $0<z<6$  \citep{Dijkstra2013}.

The observational estimation by \cite{Hayes2010} was based on blind
surveys of the H$\alpha$ and Lyman $\alpha$ line. Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
  esc}=(10.7\pm 2.8)\%$ if a different dust correction is used.

They also showed that that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$.

\cite{Dijkstra2013} used a similar principle to derive their results. They
compared observationally derived star formation functions to LAE
luminosity functions. At $z\sim 3.0$ they derive an effective escape
fraction of $f_{\rm esc}=(17\pm 5)\%$ could be interpreted as an
occupation fraction $f_{\rm occ}\sim 0.2$.  We consider a success of
our method the fact that we find that most of the consistent models
show a low occupation fraction.

@@

We also find that an ACF analysis on a single data-set is not enough to rule
out models with a high occupation fraction $f_{\rm occ}>0.3$, which
represent almost one fourth of our best models, coinciding with a wide
range in halo masses $\Delta M>1.0$ dex. These models cannot be
considered unfavorable based on a clustering analysis only.

@@

We conclude this section by noting that the uncertainties on
the preferred masses in \citep{Gawiser07} and \cite{Ouchi2010} are
found with in the intervals $M_{\rm min}$ and $M_{\rm max}$ of our
models. Under the light of our model, this implies that detected LAEs
must be absent from the most massive dark matter halos at that
redshift.

@@

In our results, all the preferred models have a halo mass range lower
than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considered in
abundance matching at $z=3$. Thus confirming the expectations of LAEs
to be found in less massive halos than those for LBGs.

A detailed analysis of the spectral and photometric properties of LAEs
coupled to the kind of analysis performed in this paper can be a guide
in the study of the properties of low mass dark matter halos at
$z=3.1$, extending the capabilities of abundance matching methods.

@@

There are two important caveats for the work presented here. The first is the
assumption of a single LAE per dark matter halo. It is expected
for sub-halos in the simulation to host satellited galaxies. However,
it has been found in analysis based on the shape of the correlation
function \citep{Jose2013b} that satellite galaxies are not a dominant
population, making our initial approximation a reasonable one.

The second caveat are the precise values for the mass intervals. These
numbers are defined from the halos defined in using the BDM halo
finder with a density threshold of 200 times the critical
density. Different halo finders and definitions for the detection
density threshold can yield different masses up to a factor. For
instance a Friends-of-Friends algorithm with linking lenght $l=0.20$
times the average interparticle distance finds halos on average $1.4$
times more massive than BDM halos \citep{Bolshoi}. Therefore, the mass
values for $M_{\rm min}$ and $M_{\rm max}$ must be considered exact
within $\sim 0.2$ dex.

@@

All the software, raw data and processed data to produce the results
and plots in this paper are publicly available in a github
repository \footnote{https://github.com/forero/CosmicVarianceLAES}. Most
of the code to produce the plots can be found as an Ipython notebook
\citep{IPython} in the same repository.

@@

\section*{Acknowledgments} 
J.E.F-R thanks the hospitality of Changbom Park and the Korea
Institute for Advanced Study where the first full draft of this paper
was completed. The authors also thank Peter Laursen, Paulina Lira and
Alvaro Orsi for helpful comments on the physical interpretation and
presentation of our results.

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.1 &10.2 & 0.1\\
10.3 &10.5 & 0.1\\
10.4 &10.7 & 0.1\\
10.5 &10.6 & 0.3\\
10.5 &10.9 & 0.1\\
10.5 &11.0 & 0.1\\
10.6 &11.2 & 0.1\\
10.6 &11.4 & 0.1\\
10.6 &11.7 & 0.1\\
10.7 &11.0 & 0.2\\
10.8 &11.2 & 0.2\\
10.8 &11.3 & 0.2\\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
10.6 &10.7 &0.4\\
10.8 &10.9 &0.6\\
10.8 &11.0 &0.4\\
10.9 &11.0 &0.8\\
10.9 &11.0 &0.9\\
10.9 &11.1 &0.5\\
11.0 &11.1 &1.0\\
11.1 &11.3 &0.8\\
11.2 &11.6 &0.6\\
11.2 &12.2 &0.5\\
11.3 &11.7 &0.9\\\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second
  family of models. Narrow mass range $\Delta M\leq 1.0$dex and high occupation fraction $f_{\rm occ}>0.3$.}
\end{table}

>>>>

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field size by
constructing mock fields from a large cosmological N-body
simulation matching the observational geometries. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
one LAE with a probability $f_{\rm occ}$.  We find that the observational information on the number density restricts the minimum mass to a
range $10^{10}\hMsun < M_{\rm min}< 10^{11.5}\hMsun$ leaving all the
other parameters unrestricted, while the clustering information puts a
tight constraint of $M_{\rm   max}<10^{12}\hMsun$. This gives support
to the idea that the most massive dark matter halos at that epoch do
not host the brightest LAEs.  However, none of these observations is
able to constrain the occupation fraction. It is always possible to
find a model that is consistent with observations and has any desired
occupation fraction in the range $0.1\leq f_{\rm occ}\leq
1.0$. We also find that all models have a narrow mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than 1.0 dex,
with the vast majority in the range $\Delta M<0.5$ dex, meaning that
there is only a factor of $3$ in mass between the minimum and maximum
halo mass. We divide the best models into families of low and high occupation
fraction with a transition around $f_{\rm occ}\leq 0.3$. These two
families are almost disjoint in their values of $M_{\rm min}$. Low
occupation fraction occurs below a threshold of $M_{\rm th}=
10^{10.8}\Msun$, while high occupation fractions are present in
models with $M_{\rm min}>M_{\rm th}$. This represents an unconclusive response as
to which is the occupation fraction for LAEs at $z=3.1$. A definite
answer requires a detailed physical model for the  connection between
dark matter, star formation and the escape of \ly radiation. That kind
of modelling should also provide a plausible explanation for the
narrow range in mass $\Delta M<1.0$ dex derived here for the halos
hosting LAEs at $z=3.1$.

@@

We note that we use $15\times 12=144$ mock fields out of the total of $210$
available sub-volumes. The reason is that the {\texttt match}
method imposes constraints on the way the $7$ fields mimicking the
SSA22 can be distributed. This restriction makes unusuable some of the
sub-volumes in the box. We decide to keep the number of mock surveys
fixed to $15$ also for the {\texttt random} method in order to allow a
fair comparison between the two methods.

@@

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
both for the comparisong against \cite{Hayashino2004} and
\cite{Ouchi2010}. To make this selection we consider that
a model is consistent with observations if there is a $1-\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. We clearly see from this Figure that the conditions imposed
by \cite{Hayashino2004} are the tightest. Comparing this Figure with
the results shown in Figure \ref{fig:restriction_mock} we see that
practically all models with $M_{\rm max}>10^{12}$ are removed. On the
other hand the comparison against \cite{Ouchi2010} does not
substantially reduce the number of models.

At this point we take the most strict selection criterio and keep the
models that are consistent with both observational constraints. This
basically reduces the selection to the models already restricted by
the data in \cite{Hayashino2004} as presented in the lower panels of Figure
\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
this comparison is that clustering information is able to put
meaningful constraints on the values of $M_{\rm max}$. However, the
possible values for the occupation fraction are still in the initial
range $0.1\leq f_{\rm occ}\leq 1$.

@@

In the Results Section we start by matching the rough numbers for the
galaxy surface number density. This sets the median mass of all
successful models to the broad range $(10^{10}-10^{12})$ \hMsun for
$M_{\rm min}$ and $M_{\rm max}$. We include additional criteria on the
number of mock surveys that must be consistent observations
and the information from the angular correlation function, reducing
the number of feasible models. We end up with $\sim 25$ models out of
the initial $9000$ possible combination of parameters.

In order to make a physical interpretation of these models we use 
the halo mass range, defined as $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm  min}$, together with the occupation fraction $f_{\rm
  occ}$ to classify all the successful models into two families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
  dex: 12 models. 
\item[(2)] High $f_{\rm occ}> 0.3$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
  low $\Delta M\leq 1.0$: 11 models 
\end{itemize}

The full list of paramenter in the two families is summarized in Table
\ref{table:firstfamily} and Table \ref{table:secondfamily}. We do not
have a clear majority of any family. This leads us to the following
two conclusions. First, the occupation fraction cannot be constrained
based on clustering anaylsis. Second, the halos hosting LAEs have a
narrow mass range.

The existence of a narrow mass rango for halo masses has different
possible explanations. A cut at the low mass end $M_{\rm min}$ can be
interpreted in terms of the minimal halo star formation rate needed to
produce the minimal \ly  luminosity to be above a given detection
threshold.  However, under the reasonable assumption of star formation
rate increasing with halo mass, the cut at higher halo masses requires
a different justification. There are two complementary physical
scenarios that can provide it.

@@

A second scenario is that larger systems have more extended gaseous
envelopes which due to resonance effects of the \ly line, can induce a
low surface brightness and a broader line, making these systems less
observable in narrow band filter surveys
\citep{Laursen2009,Zheng2010}.

The preference for narrow $\Delta M$ ranges to host LAEs 
and the small presence of reasonable models with $M_{\rm max}>
10^{12}$\hMsun also follows theoretical and observational
insights for high-z galaxies where the most massive systems are not
bright \ly sources \citep{ForeroRomero2012,Shapley2003}.

@@

Theoretical intepretations of blind galaxy surveys at $z=2.2$ find a
volume weighted escape fraction $f_{\rm esc}\sim 0.1-0.2$
\cite{Hayes2010}, similar results are obtained in a recent theoretical
study of observational data in a wide redshift range $0<z<6$
\citep{Dijkstra2013}.

\cite{Hayes2010} showed that the luminosity function for
LAEs at $z=2.2$ is consistent with the escape fraction being constant
for every galaxy regardless of its luminosity. From this results they
derive that almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. \cite{Dijkstra2013} uses similar
methods to find an average \ly escape fraction in high-z galaxies,
they conclude that there is a range in luminosity where the escape
fraction they derive at $z\sim 3.0$, $f_{\rm esc}=(17\pm 5)\%$, could
be interpreted as an occupation fraction $f_{\rm occ}\sim 0.2$.

We consider a success that our model indeed includes such low
occupation fraction models. The observational evidence from galaxy
surveys seem to disfavor the second family of models with high
occupation fractions. Nevertheless, it remains a task for galaxy
formation models to explain the mass range $\Delta M<0.5$ in the models.

@@

We also find that an ACF analysis on a single data-set is not enough to rule
out models with a high occupation fraction $f_{\rm occ}>0.3$, which
represent half of our best models. These models cannot be
considered unfavorable based on a clustering analysis only, it
requires additional information from galaxy surveys, as we have
presented in the previous section.

@@

We conclude this section by noting that the uncertainties on
the preferred masses in \citep{Gawiser07} and \cite{Ouchi2010} are
found with in the intervals $M_{\rm min}$ and $M_{\rm max}$ of our
models.

@@

In our results, all the preferred models have a halo mass range lower
than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considered in
abundance matching at $z=3$. This confirms once more the expectations
that most of  LAEs are to be found in less massive halos LBG hosts.A
detailed analysis of the spectral and photometric properties of LAEs
coupled to the kind of analysis performed in this paper can be a guide
in the study of the properties of low mass dark matter halos at
$z=3.1$, extending the capabilities of abundance matching methods.

@@

There are two important caveats for the work presented here. The first is the
assumption of a single LAE per dark matter halo. This contradicts the
general expectation of dark matter sub-halos in the simulation to host
satellite galaxies. However, it has been found in analysis based on
the shape of the correlation function \citep{Jose2013b} that satellite
galaxies are not a dominant population, making our initial
approximation a reasonable one. Therefore we think that it is not
crucial to include the effect of satellites in the model.

The second caveat are the precise values for the mass intervals. These
numbers are defined from the halos defined in using the BDM halo
finder with a density threshold of 200 times the critical
density. Different halo finders and definitions for the detection
density threshold can yield different masses up to a factor. For
instance a Friends-of-Friends algorithm with linking lenght $l=0.20$
times the average interparticle distance finds halos on average $1.4$
times more massive than BDM halos \citep{Bolshoi}. Therefore, the mass
values for $M_{\rm min}$ and $M_{\rm max}$ should not be considered exact
within less than $\sim 0.2$ dex.

@@

All the software, raw and processed data to produce the results
and plots in this paper are publicly available in a github
repository \footnote{https://github.com/forero/CosmicVarianceLAES}. Most
of the code to produce the plots can be found as an Ipython notebook
\citep{IPython} in the same repository.

@@

\section*{Acknowledgments} 
J.E.F-R thanks the hospitality of Changbom Park and the Korea
Institute for Advanced Study where the first full draft of this paper
was completed. The authors also thank Peter Laursen, Paulina Lira, 
Alvaro Orsi and Mark Dijkstra for helpful comments on the physical
interpretation and presentation of our results.

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.1 &10.2 & 0.1 & 0.1\\
10.3 &10.5 & 0.1 & 0.2\\
10.4 &10.7 & 0.1 & 0.3\\
10.5 &10.6 & 0.3 & 0.1\\
10.5 &10.9 & 0.1 & 0.4\\
10.5 &11.0 & 0.1 & 0.5\\
10.6 &11.2 & 0.1 & 0.6\\
10.6 &11.4 & 0.1 & 0.8\\
10.6 &11.7 & 0.1 & 1.1\\
10.7 &11.0 & 0.2 & 0.3\\
10.8 &11.2 & 0.2 & 0.4\\
10.8 &11.3 & 0.2 & 0.5\\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.6 &10.7 &0.4 & 0.1\\
10.8 &10.9 &0.6 & 0.1\\
10.8 &11.0 &0.4 & 0.2\\
10.9 &11.0 &0.8 & 0.1\\
10.9 &11.0 &0.9 & 0.1\\
10.9 &11.1 &0.5 & 0.2\\
11.0 &11.1 &1.0 & 0.1\\
11.1 &11.3 &0.8 & 0.2\\
11.2 &11.6 &0.6 & 0.4\\
11.2 &12.2 &0.5 & 1.0\\
11.3 &11.7 &0.9 & 0.4\\\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second
  family of models. Narrow mass range $\Delta M\leq 1.0$dex and high occupation fraction $f_{\rm occ}>0.3$.}
\end{table}
